Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-03-18 thesis-main.tex
Switch from input to include to use includeonly

\title{Optimizing and Incrementalizing Collection Queries by AST Transformations}
\author{Paolo G. Giarrusso}
\begin{document}
\maketitle
\input{pldi14/agda}

@@

\input{chap-intro}

@@

\input{aosd13/graphs/evalResLos}
\input{aosd13/paperBody}

\part{Incrementalization}
\label{part:incr}
\input{pldi14/sec-preliminaries}
\input{pldi14/sec-intro}

% Include either-or, one includes the other.
%\input{change-theory-reconstruct}
\input{pldi14/sec-change-theory}
\input{pldi14/sec-change-equiv}

\input{pldi14/sec-differentiate}
\input{pldi14/sec-practice}
\input{pldi14/sec-concl}

% Appendixes, to integrate.
% \input{pldi14/sec-evaluation}
% \input{pldi14/sec-addendum}

\begin{oldSec}
\input{pldi14/sec-STLC-correct}
\end{oldSec}

\begin{oldSec}
\input{pldi14/sec-informal}
\end{oldSec}

\input{new-stuff}
\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

>>>>

\title{Optimizing and Incrementalizing Collection Queries by AST Transformations}
\author{Paolo G. Giarrusso}

% Only for development.
%
% Requires that other files are compiled with include, and can only be used in
% incremental runs: a first run has to be made without includeonly.
%
% \includeonly{pldi14/sec-preliminaries,pldi14/sec-intro}
%
% Also, include can add extra page breaks, so maybe switch back to input at the end.
% From http://web.science.mq.edu.au/~rdale/resources/writingnotes/latexstruct.html.
\begin{document}
\maketitle
\input{pldi14/agda}

@@

\include{chap-intro}

@@

\include{aosd13/graphs/evalResLos}
\include{aosd13/paperBody}

\part{Incrementalization}
\label{part:incr}
\include{pldi14/sec-preliminaries}
\include{pldi14/sec-intro}

% Include either-or, one includes the other.
%\include{change-theory-reconstruct}
\include{pldi14/sec-change-theory}
\include{pldi14/sec-change-equiv}

\DeclareFixedFootnote{\EmptyEmptyNote}{%
To evaluate a closed term $t$, we need no environment entries, so
the empty environment $\EmptyEnv$ suffices:
$\EvalWith*{t}{\EmptyEnv}$ is the value of $t$ in the empty environment, and
$\;\EvalIncSmashWith*{t}{\EmptyEnv}{\EmptyEnv}$
is the value of $t$ using the change semantics, the empty environment and the empty change
environment.}

\include{pldi14/sec-differentiate}
\include{pldi14/sec-practice}
\include{pldi14/sec-concl}

% Appendixes, to integrate.
% \include{pldi14/sec-evaluation}
% \include{pldi14/sec-addendum}

\begin{oldSec}
\include{pldi14/sec-STLC-correct}
\end{oldSec}

\begin{oldSec}
\include{pldi14/sec-informal}
\end{oldSec}

\include{new-stuff}
\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
